\documentclass[a4paper,fontset=ubuntu,12pt]{ctexart}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage{listings}
\usepackage{comment}
\title{Rules for the fag slave(Scout)}
%\author{Jack King}
%\date{\today}
\begin{document}
\maketitle

\begin{comment}

\begin{itemize}
\item 贱狗存在的唯一意义就是跪在主人脚下用狗嘴伺少爷，贱狗只能用狗嘴伺候少爷的身体和鞋袜， 未经少爷允许，不能用狗爪子帮忙。
\item 贱狗不能用使用“你”，“我”等词汇，必须称呼主人为“爷“，”少爷”；称呼自己为“奴才”，“贱狗”。
\item 贱狗要发自内心地崇拜少爷， 努力伺候少爷让少爷爽，具体表现在：
    \begin{itemize}
        \item 在少爷脚下闻舔鞋袜时保持深呼吸好好感受少爷的脚味，少爷使用贱狗当尿壶时贱狗要仔细闻并品尝圣水，心里要想着自己有多渴望喝到它崇拜的帅主人的尿，贱狗能舔到少爷的脚喝到少爷的尿是贱狗的福气。
        \item 贱狗每次伺候完少爷都要心怀感激地磕头谢恩，边磕头边说“谢谢少爷赏奴才舔少爷的帅脚“，谢谢少爷用龙根草奴才的狗嘴”等。
        \item 贱狗在回答少爷的问话时必须表现出自己的下贱，少爷玩儿到兴头上贱狗要主动求少爷玩儿自己，比如“求少爷赏奴才舔龙根“，”喝圣水”等。贱狗在发骚时必须口齿清晰，不能因为害羞说得很轻或者不说话。要牢记自己就是少爷脚下的一条狗，生下来就是跪求伺候少爷的命。
        \item 用狗嘴伺候少爷时要时刻想着怎么让少爷玩儿得更爽，比如舔少爷的脚趾缝时舔得少爷很爽，贱狗就要记住当时是怎么舔的，这样慢慢提高自己的口活。 贱狗在舔少爷的帅脚和龙根时必须努力用嘴唇包裹住狗牙，以免少爷觉得不适。 在深喉的时候喉咙要不断得吞咽，以便用狗喉咙按摩少爷的龙根。被少爷草嘴草到干呕时也不能怠慢，要确保狗嘴包裹住少爷的龙根。如果做得不好要做好挨少爷揍的准备。
        \item 少爷在揍贱狗出气时贱狗要主动配合，比如主动把脸凑到少爷脚边让少爷踹，被踹后及时爬回少爷脚下等着少爷踹。如果少爷踹累了，贱狗主动磕头谢恩，然后闻舔少爷的鞋袜，舔少爷的脚底来表达对少爷的崇拜，让少爷感受到征服的快感。
    \end{itemize}
\item 贱狗的日常行为规范：
    \begin{itemize}
        \item 早上起床后做早间崇拜，嘴里含着少爷昨天穿过的袜子，脸伸到少爷的球鞋里感受少爷的脚味。 然后给少爷磕头，亲舔少爷的脚底，请少爷下床。
        \item 少爷上厕所时贱狗应该跪在马桶前，听从少爷的命令给少爷磕头，舔龙根，或者舔脚，含着少爷的龙根时贱狗要在马桶前深呼吸，好好地感受少爷的黄金的香味， 并磕头感谢少爷赏贱狗闻黄金。
        \item 少爷会买来早饭，用脚喂贱狗吃，贱狗要心存感激地把少爷的帅脚舔舐干净，并磕头谢恩。除了少爷的洗脚水和圣水外，贱狗不能喝其他的水。
        \item 贱狗如果有上厕所的需求，应先判断如果憋着是否会影响到伺候少爷的能力，如会影响，应该及时求少爷让贱狗上厕所。 上完厕所后应该爬回少爷脚边给少爷磕头谢恩，并心存感激地继续好好伺候少爷。
        \item 少爷在上网打游戏时让贱狗舔脚，舔龙根，舔肛。贱狗必须安静地卖力地伺候少爷，狗舌头勤快地来回洗刷让少爷爽。
        \item 少爷外出时贱狗要听从少爷的吩咐，在家闻舔少爷的鞋袜， 或者在家熟悉少爷圣水的味道和口感。舔鞋的时候不光要把鞋底鞋面舔干净，还要把鞋垫拿出来用狗舌头把少爷脚汗味道都舔到肚子里去。舔完鞋后贱狗要主动去卫生间漱口，狗嘴洗干净后才能舔少爷的龙根。贱狗要多关注少爷发给贱狗的微信，少爷回来时贱狗应该提前跪在门口迎驾。
        \item 少爷在揍贱狗的时候贱狗要表现出被揍得很惨的样子，被揍得吃不消的时候，或者被少爷玩儿得吃不消的时候，贱狗要下贱得爬到少爷脚下磕头求饶，边磕头边说“求少爷饶了贱狗的小命“，感受被少爷征服，踩在脚下的羞耻感。
        \item 少爷下午午睡时会让贱狗跪在床边给少爷舔脚，贱狗要认真仔细，用最能让少爷舒服的舔法舔舐少爷的帅脚，自动地来回把少爷的两只脚都伺候好，直到少爷睡着。少爷在睡觉时贱狗应该好好休息保存体力，以便在少爷起床后可以好好伺候少爷。
        \item 晚上睡前少爷会爽草狗嘴直到草射，贱狗要努力地配合少爷让少爷草嘴草得爽。贱狗白天伺候得好，少爷会奖励贱狗睡在少爷的脚下或者胯下，贱狗必须好好伺候少爷的帅脚和龙根。半夜少爷可能会想草狗嘴把贱狗踹醒，贱狗必须快速恢复清醒，并努力地伺候好少爷的龙根。
        \item 少爷在刚开始调教贱狗当尿壶时，会让贱狗拿着杯子张开狗嘴尿在贱狗的嘴里，贱狗要好好感受少爷圣水的口感和香味。一般刚开始贱狗还喝不下去会呛到，因此圣水会从从贱狗嘴里留到杯子里，贱狗要根据自己的能力控制喝下多少流下多少，以免一直在呛让少爷扫兴。在接受厕奴调教的时候贱狗要不断回想自己有多崇拜少爷，努力喝下更多的圣水。少爷尿完后，贱狗要主动把少爷的龙根舔干净， 并磕头谢恩。贱狗要不断努力，争取早日成为少爷的尿壶。
    \end{itemize}
\end{itemize}

\end{comment}

\begin{itemize}
    \item The fag slave is naturally inferior to its master, which entails:
    
        \begin{itemize}
            \item The fag must always be on its knees or on its fours when in face of its master, only except in public places or in the presence of vanilla third parties.
            
            \item The fag is not allowed to touch the master's body above waist. It is only allowed to use its mouth to serve the master's body below waist, unless having obtained special permission from master in some physically inevitable situations.
            
            \item The master likes dog slave training, so the fag should behave like a dog, e.g., walk on its fours; fetch master's shoes, socks with its mouth; rest around and sniff master's feet. 
            
            \item The fag is not allowed to do or say anything on its own will while serving its master, except answering questions from master, performing necessary actions while executing orders, or speaking out safe word. The safe word is 'stop', two hands raised up if not able to speak, and struggle with the whole body if the former two unable to perform.  
            
            \item The fag must check its telegram frequently, and responds to the master's messages within two hours except quiet hours, that is, 8 am - 11:59pm. Any violation will lead to punishment.
            
            \item The fag must be in chastity within the whole duration of this relationship, and never allowed to have any sexual contact with any other people or animals. The fag is also responsible to maintain healthy, and communicate to the master if it is in an illness condition, both physically and mentally.
            
            \item The highest responsibility of the fag is to maximize the master's pleasure to its best effort. Therefore, any sluggish behavior is regarded as dereliction of duty, which will incur punishments.
            
            \item The master owns fag's body, and is free to use it in any way for the master's pleasure. Exceptions: permanent marks, damages; extreme torture that may cause mental health problem to the slave. The fag slave is responsible to ensure its physical and mental health, by communicating faithfully its health concern to its master, if any.
            
            \item The master is free to take pics and videos of him humiliating the slave. The master owns the pics and videos, and is free to post it on his social accounts and blogs. Nonetheless, the master will ensure that this does not ruin the fag's social or career life, which is not aligned with the master's interest.
            
        \end{itemize}
    
    \item Chores: The fag is responsible to routinely clean master's socks, underwears, and sneakers with the following procedures:
        \begin{enumerate}
            \item Sniff and lick until smell on the socks, underwears, insoles are gone; and no longer tastes salty.
            \item Wash clean by hands and soap.
            \item Washing and drying machine.
        \end{enumerate}
        
    \item When the fag serves as a domestic slave in master's home, it is responsible for taking care of the master's everyday life, including and not limited to:
        \begin{enumerate}
            \item House cleaning
            \item Serve as foot rest, seat, cushion etc.
            \item Fetch lunch and dinner ordered by the master, and clean dishes afterwards.
        \end{enumerate}

\end{itemize}        

All the above rules are subject to augmentation and revision by the master.

The fag only has a binary choice, either accept all, or decline, indicating the end of the relationship.


\begin{comment}


    \item The existence of the fag is to worship the feet of his master. His mouth's purpose is to serve the master. The Fag will use his mouth to remove the master's shoes and socks. Unless given permission, he may not use his hands. %Fag's can't use words like (Seek clarification here). They must call themselves (seek clarification here). 
    \item The fag should worship his master from his heart and strive to keep the master happy with his performance. 
    \begin{itemize}
        \item He should inhale strongly when smelling the shoes and socks of his master, feel the feet of his master, be a urinal for his master. Fag should limit his consumption of liquid in preparation for service as a urinal. It's a blessing for the slave to be allowed to worship his master's feet and drink of this urine. 
        \item Everytime the slave serves his master, he will be grateful and say "Thank you for letting me worship your handsome feet." Slave will take initiative to ask permission to play with the Master such as asking him to reward the slave with his urine.
        \item Slave must be open and honest and not hold back because of shame. Slave must always remember that he is a slave at the foot of his master and he is born to beg for his life from his master. 
        \item When the slave's mouth waits for his master, he must always consider how to make his master's life better. For example, when the master's toes are sore, the master is unhappy. The slave should remember what he did to cause this and improve his technique. Slave will avoid the use of teeth on his master's penis and feet by curling his lips over them. Slave will swallow continuously when deep throating to maximize his master's pleasure.
    \end{itemize}
    

    \item Master will use his feet to provide breakfast to his slave and the slave will be grateful to clean his feet. Slave will not drink other liquid than the liquid used to clean Master's feet or his urine. If the slave needs to use the restroom, he should first ensure it will not impact his master. If it will impact, he should ask for permission and come immediately back. Slave should show gratitude for this permission and ability to continue serving his master.
    
    \item Slave will worship master's feet while he plays online games. Slave will wait quietly and dutiful keep his master's feet cool by licking back and forth. 
    
    \item When Master leaves, the slave will listen to his master's wishes, smell the master's socks and shoes, or remember the taste of the master's urine. When smelling the shoes, the slave will not only lick the soles, but take the insoles of the shoes out and lick the taste of the master's feet. Slave will gargle his mouth out in the restroom to make sure it is cleaned before he sucks his master's penis. Slave should pay more attention to the messages issued by the master such that he can be squatting at the door in anticipation of the master's return.
    
    \item When the master is angry with the slave, the slave will show a shameful appearance. When the slave can't continue any more with his task, he crawl to the feet of his master and beg for mercy. While hanging his head in shame, he will say "seeking master to spare slave's life". He will feel shame for not being able to perform.
    
    \item When master takes a nap in the afternoon, the slave will be allowed to sit bedside and service his master's feet taking care to pay attention to both feet. When the master is sleeping, the slave will rest and conserve his strength so he is ready when the master wakes up. 
    
    \item Before sleeping, the master will fuck the slave's mouth until he cums. Slave will work hard to make the master happy. If the slave performs well during the day and the master will reward the hyena to sleep at the foot of the bed. Master may want to wake up in the middle of the night and the slave will try his best to serve the master. 
    
    \item When the master trains the slave to be a urinal, he will allow the slave to hold a cup to his mouth. In the slave's mouth, the slave should feel the taste and fragrance of the master.
\end{itemize}

\end{comment}

\end{document}